---
title: "R Notebook"
output: html_notebook
---

Handling strings with R
Source
https://www.gastonsanchez.com/r4strings/cleaning.html

```{r}
install.packages('stringr')

install.packages('tidyverse')

install.packages("htmlwidgets")
```

```{r}
library(stringr)
library(tidyverse)
```
12.1 Defining character sets
```{r}
pns <- c('pan', 'pen', 'pin', 'pon', 'pun')

str_view(pns, "p[aeiou]n")

str_view(pns, "p.n")
```

```{r}
basic <- c('1', 'a', 'A', '&', '-', '^')

str_view(basic, '[0-9]')
```

```{r}
triplets <- c('123', 'abc', 'ABC', ':-)')

str_view(triplets, '[0-9][0-9][0-9]')
```

The caret "^" is one of those metacharacters that have more than one meaning depending on where it appears in a pattern. If you use a caret in the first position inside a character set, e.g. [^aeiou], it means negation. In other words, the caret in [^aeiou] means “not any one of lower case vowels.”

```{r}
basic <- c('1', 'a', 'A', '&', '-', '^')
```

To match those elements that are NOT upper case letters, you define a negative character range "[^A-Z]":

Match everything except the capital letters
```{r}
str_view(basic, '[^A-Z]')
```

```{r}
str_view(basic, '[A-Z^]')
```
13. Anchors formatting
```{r}
university <- c(
  "University of Southern California", 
  "California State University", 
  "Stanford University", 
  "University of California, Berkeley")

university
```
starts with university
```{r}
str_detect(university, "^University")
```
ends with university
```{r}
str_detect(university, "University$")
```

```{r}
university <- c(
  "University of Southern California
  \nCalifornia State University
  \nStanford University
  \nUniversity of California, Berkeley\n")

cat(university)
```

```{r}
str_extract_all(university, regex("[A-z ]*University$", multiline = TRUE))
```
Quantifiers

In the following example, let us try to extract all those names that contain more than 4 characters and less than 7 characters.
```{r}
student_names <- c("Lee", "Carol", "Sameer", "Luca", "Rajan", "George Jr.")
```

```{r}
str_extract(student_names, "^[A-z]{5,7}$" )
```
In the last example, if we want to extract names that contain e or u we could follow this simple implementation . Points to note here:

Character set [eu] could appear 1 or more times so we use quantifier +.

.* matches 0 or any number of characters where . is a wildcard dot and * represents the quantifier 0 or many

Pattern .*[eu]+.* looks for 1 or more numbers of [eu] that can be preceeded/followed by any number of other characters.
```{r}
str_detect(student_names, regex("[eu]+"))
```
Consider an example where we would like to extract only strings with two names separated by a whitespace. For illustrative purpose, the strings end with a whitespace.
```{r}
student_names <- c(
  "Lee Zhang ", 
  "Carol Roberts ", 
  "Sameer ", 
  "Luca ", 
  "Rajan ", 
  "George Smith Smith ")
```

```{r}
str_extract(student_names, regex("([A-z]+[ ]){3}"))
```
Data Cleaning
```{r}
install.packages('rvest')
library(rvest)
```

```{r}
wiki_jump <- 'https://en.wikipedia.org/wiki/Men%27s_long_jump_world_record_progression'

long_jump <- read_html(wiki_jump)
tbl <- html_table(html_node(long_jump, 'table'))
```

```{r}
str(tbl, vec.len = 1)
```

```{r}
tbl$Mark[1]
```

```{r}
substr(tbl$Mark[1], start = 1, stop = 4)
```

```{r}
meters <- as.numeric(substr(tbl$Mark, start = 1, stop = 4))
meters
```
Let's try to do this using a pattern

[0-9]\\.[0-9][0-9]
```{r}
str_detect(tbl$Mark[1], pattern = "[0-9]\\.[0-9][0-9]")
```

```{r}
str_extract(tbl$Mark, pattern = "[0-9]\\.[0-9][0-9]")
```
Extract a country
```{r}
tbl$Athlete[1]
```

```{r}
substr(tbl$Athlete, nchar(tbl$Athlete)-4, nchar(tbl$Athlete))
```

```{r}
country <- substr(tbl$Athlete, nchar(tbl$Athlete)-3, nchar(tbl$Athlete)-1)
country
```
Cleaning Dates
```{r}
tbl$Date[1:5]
```

```{r}
date1 <- tbl$Date[1]
date1
```


```{r}
str_match(date1, pattern = "\\[1\\]")
```

```{r}
str_replace(date1, pattern = "\\[1\\]", replacement = '')
```

```{r}
dates <- str_replace(tbl$Date, pattern = "\\[1\\]", replacement = "")
dates <- str_replace(dates, pattern = "\\[[3-5]\\]", replacement = "")
dates
```


```{r}
str_extract(dates, pattern = "[A-Z][a-z][a-z][a-z]")
```


```{r}
month_names <- str_extract(dates, pattern = "[A-Z][a-z]+")
month_names
```

```{r}
str_extract(dates, pattern = "[0-9]+")
```
for a year
```{r}
str_sub(dates, start = -4)

str_extract(dates, pattern = '[0-9][0-9][0-9][0-9]')
```

```{r}
str_extract(dates, pattern = "[0-9]+$")
```

```{r}
str_extract(tbl$Athlete, pattern = "[A-Z][a-z]+")
```
The pattern "[A-Z][a-z]+" fails to match the name of the fourth athlete DeHart Hubbard (USA). One way to match an optional upper case in the third position is with the following pattern: "[A-Z][a-z][A-Z]?[a-z]


```{r}
str_extract(tbl$Athlete, pattern = "[A-Z][a-z][A-Z]?[a-z]+")
```
An alternative option is to use the word character class \\w repeated one or more times: "\\w+"
```{r}
str_extract(tbl$Athlete, pattern = "\\w+")
```
In reality, we want both the apostrophe and the second upper case letters to be optional, so we need to add quantifiers "?" to both of them:
```{r}
str_extract(tbl$Athlete, pattern = "[A-Z][a-z][A-Z]?[a-z]+ [A-Z]'?[A-Z]?[a-z]+")
```
. So we also need to include upper case letters in the character set: "[a-zA-Z\\-]"
```{r}
str_extract(tbl$Athlete, pattern = "[A-Z][a-z][A-Z]?[a-z]+ [A-Z]('[A-Z])?[a-zA-Z\\-]+")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```