---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("MetBrewer")
library(MetBrewer)
```

```{r}
devtools::install_github("gadenbuie/ggpomological")
library(ggpomological)
```

```{r}
library(tidyverse)
library(janeaustenr)
library(tidytext)

#install.packages("forcats")
library(forcats)
```
## theme
```{r}
## 
my_pretty_theme <- theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        # Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Italic, smaller, grey caption that is left-aligned
        plot.caption = element_text(face = "italic", size = rel(0.7), 
                                    color = "grey70", hjust = 0),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold, slightly larger facet titles that are left-aligned for the sake of repetition
        strip.text = element_text(face = "bold", size = rel(1.1), hjust = 0),
        # Bold axis titles
        axis.title = element_text(face = "bold"),
        # Add some space above the x-axis title and make it left-aligned
        axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
        # Add some space to the right of the y-axis title and make it top-aligned
        axis.title.y = element_text(margin = margin(r = 10), hjust = 1),
        # Add a light grey background to the facet titles, with no borders
        strip.background = element_rect(fill = "grey90", color = NA),
        # Add a thin grey border around all the plots to tie in the facet titles
        panel.border = element_rect(color = "grey90", fill = NA))
```


# 4 Relationships between words: n-grams and correlations

```{r}
austen_bigrams  <- austen_books() %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)
austen_bigrams
```

```{r}
austen_bigrams %>% count(bigram, sort = TRUE)
```
## @separate function - splits a column into multiple based on a delimiter. 

This lets us separate it into two columns, “word1” and “word2”, at which point we can remove cases where either is a stop-word.
```{r}
bigrams_filtered  <- austen_bigrams %>%
  separate(bigram, c('word1', 'word2'), sep = " ") %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)
```

```{r}
# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
```

## @ unite function
```{r}
bigrams_united <- bigrams_filtered %>% 
  unite(bigram, word1, word2, sep = " ")

bigrams_united
```
## use bind_tf_idf for bigrams
```{r}
bigram_tf_idf <- bigrams_united %>%
  count(book, bigram) %>%
  bind_tf_idf(bigram, book, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf
``` 

```{r}
extrafont::font_import("Homemade Apple")
```


```{r fig.height=8}
bigram_tf_idf %>%
  group_by(book)%>%
  slice_max(tf_idf, n = 10) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(bigram,tf_idf) , fill = book))+
  geom_col(show.legend = FALSE)+
  facet_wrap(~book, ncol = 2, scales = "free")+
  theme_pomological("Homemade Apple", 16)+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
  
```
## 4.1.3 Using bigrams to provide context in sentiment analysis
```{r}
bigrams_separated <- austen_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")


bigrams_separated %>%
  filter(word1 == "not") %>%
  count(word1, word2, sort = TRUE)
```


```{r}
AFINN <- get_sentiments("afinn")

AFINN
```


```{r}
not_words <- bigrams_separated  %>%
  filter(word1 == "not") %>%
  inner_join(AFINN, by = c(word2 = "word")) %>% 
  count(word2, value, sort = TRUE)

not_words
```

```{r}
not_words %>%
  mutate(contribution = n * value) %>%
  arrange(desc(abs(contribution))) %>%
  head(20) %>%
  mutate(word2 = reorder(word2, contribution)) %>%
  ggplot(aes(n * value, word2, fill = n * value > 0)) +
  geom_col(show.legend = FALSE) +
  labs(x = "Sentiment value * number of occurrences",
       y = "Words preceded by \"not\"")+
  theme_bw()+
  scale_fill_manual(values=met.brewer("Greek", 2))
```


```{r}
negation_words <- c("not", "no", "never", "without")

negated_words <- bigrams_separated %>%
  filter(word1 %in% negation_words) %>%
  inner_join(AFINN, by = c(word2 = "word")) %>%
  count(word1, word2, value, sort = TRUE)
```

## 4.1.4 Visualizing a network of bigrams with ggraph

```{r}
install.packages("igraph")
install.packages("ggraph")

library(igraph)
library(ggraph)
```

```{r}
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# new bigram counts:
bigram_counts <- bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)
```


```{r}
bigram_graph <- bigram_counts  %>%
  filter(n>20) %>%
  graph_from_data_frame()
```
Continue: https://www.tidytextmining.com/ngrams.html#using-bigrams-to-provide-context-in-sentiment-analysis
```{r}

```

```{r}

```


```{r}

```


```{r}

```

```{r}

```