---
title: "R Notebook"
output: html_notebook
---

The Tidy text format

source https://www.tidytextmining.com/tidytext.html

### 1.2 The unnest_tokens function
```{r}
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")

text
```
```{r}
install.packages('tidytext')
```

```{r}
library(tidyverse)

library(tidytext)
library(stringr)

text_df <- tibble(line = 1:4, text = text)
```

```{r}
text_df %>% 
  unnest_tokens(word, text)
```

```{r}
install.packages('janeaustenr')
library(janeaustenr)
```

```{r}
original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, 
                                     regex("^chapter [\\divxlc]",
                                           ignore_case = TRUE)))) %>%
  ungroup()

original_books
```

```{r}
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books
```
Remove stop words
```{r}

data(stop_words)

tidy_books <- tidy_books %>%
  anti_join(stop_words)

```

```{r}
tidy_books %>%
  count(word, sort = TRUE)
```

```{r}
tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600)  %>%
  mutate(word = reorder(word, n))  %>%
  ggplot(aes(n, word)) +
  geom_col(fill = 'navyblue') + 
  labs(y = NULL) +
  theme_classic()
```

```{r}
install.packages('gutenbergr')
```

```{r}
library(gutenbergr)
hgwells <- gutenberg_download(c(35, 36, 5230, 159))

tidy_hgwells <- hgwells %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```
```{r}
tidy_hgwells %>%
  count(word, sort = TRUE)
```
Now let’s get some well-known works of the Brontë sisters, whose lives overlapped with Jane Austen’s somewhat but who wrote in a rather different style. Let’s get Jane Eyre, Wuthering Heights, The Tenant of Wildfell Hall, Villette, and Agnes Grey. We will again use the Project Gutenberg ID numbers for each novel and access the texts using gutenberg_download().

```{r}
bronte <- gutenberg_download(c(1260, 768, 969, 9182, 767))

tidy_bronte <- bronte %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)
```

```{r}
tidy_bronte %>%
  count(word, sort = TRUE)
```

Now, let’s calculate the frequency for each word for the works of Jane Austen, the Brontë sisters, and H.G. Wells by binding the data frames together. We can use pivot_wider() and pivot_longer() from tidyr to reshape our dataframe so that it is just what we need for plotting and comparing the three sets of novels.
```{r}
library(tidyr)

frequency <- bind_rows(mutate(tidy_bronte, author = "Brontë Sisters"),
                       mutate(tidy_hgwells, author = "H.G. Wells"), 
                       mutate(tidy_books, author = "Jane Austen")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(author, word) %>%
  group_by(author) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = author, values_from = proportion) %>%
  pivot_longer(`Brontë Sisters`:`H.G. Wells`,
               names_to = "author", values_to = "proportion")

frequency
#> # A tibble: 57,820 × 4
#>    word    `Jane Austen` author          proportion
#>    <chr>           <dbl> <chr>                <dbl>
#>  1 a          0.00000919 Brontë Sisters  0.0000319 
#>  2 a          0.00000919 H.G. Wells      0.0000150 
#>  3 a'most    NA          Brontë Sisters  0.0000159 
#>  4 a'most    NA          H.G. Wells     NA         
#>  5 aback     NA          Brontë Sisters  0.00000398
#>  6 aback     NA          H.G. Wells      0.0000150 
#>  7 abaht     NA          Brontë Sisters  0.00000398
#>  8 abaht     NA          H.G. Wells     NA         
#>  9 abandon   NA          Brontë Sisters  0.0000319 
#> 10 abandon   NA          H.G. Wells      0.0000150 
#> # … with 57,810 more rows
```

```{r}
install.packages('scales')
library(scales)
```

```{r fig.height=10, fig.width=10}
# expect a warning about rows with missing values being removed
ggplot(frequency, aes(x = proportion, y = `Jane Austen`, 
                      color = abs(`Jane Austen` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Jane Austen", x = NULL)
```


```{r}
cor.test(data = frequency[frequency$author == "Brontë Sisters",],
         ~ proportion + `Jane Austen`)
```

```{r}
cor.test(data = frequency[frequency$author == "H.G. Wells",], 
         ~ proportion + `Jane Austen`)
```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```
```{r}

```

```{r}

```

```{r}

```

```{r}

```vv